---
title: "Group 1 Report"
author: "Julian Cornea, Kim Ferres, Jan Löffelmann"
date: "23-05-2019"
output:
  bookdown::html_document2:
    toc: yes
    toc_float: true
    theme: flatly
---

```{r importingMyLibraries, echo=F, results = "hide", message=F, warning=F}
  #    ^ only output, not coding
  #cmd+alt+i --> for r coding
  #load libraries
  library(diffobj)
  library(gridExtra)
  library(dplyr)
  library(janitor)
  library(ggplot2)
  library(ineq)
  library(chron)
  library(maps)
  library(tidyr)
  library(plyr)
  library(ggrepel)
  library(knitr)
  library(stringr)
```

#About the Data {#data}

The available data comes from an online shop, which sells beauty products. There are two datasets given: One with data about customer orders and another with data about customer clicks on the website.

The orders dataset consists of one row for each customer order in the time periode from the 28. January 2000 to the 3. March 2000. The data contains values such as the number of product units ordered, the total order amount, payment information, the manufacturer and brand names of the ordered products and social data about the customer, as by example his location or age.

The clicks dataset contains data referring to customer clicks on the website of the given company. Therefore, it is composed of data such as the timestamp of a click, the session length and the name of the clicked product, as well as the product category it belongs to. In this way the whole session course of a customer can be illustrated through the data.

Both datasets share a considerable amount of columns. However, since not every click results in an order and since a session consists normally of more than one click, the contents differ significantly.

#Task Description {#task}

The project's task is to analyze the dataset, especially by creating plots and statistical tables for the data, that is suspected to be relevant for the online shop in some way. 

<!-- TODO: Task description of the modelling task -->
Additionally, a model has to be constructed to predict...

#Cleaning the Data {#cleaning}

Before we started cleaning the data, we copied it to the folder "0 Data". The reason for this was to avoid accidentally altering the original dataset due to the clear logistical separation of the edited datasets from the original ones. The cleaned data and further forms of the datasets were also saved to this folder. Before explaining the cleaning process, it makes sense to get an overview of the content of the aforementioned folder. It can be described as follows:

* Each file has a suffix depending on what language was used for creating it. Files created with a Python script have the suffix "_P", while files created with R have the suffix "_R". 
* For both datasets three types of files are created: 
    + A copy of the original dataset (e.g. "order_data_R.csv")
    + A cleaned version of that dataset (e.g. "order_data_cleaned_R.csv")
    + A smaller version of the cleaned data, which allows quick viewing and testing of the technical functionality of the coding (e.g. "order_data_small_R.csv")

<!-- TODO: Task description of the modelling task -->
    
The cleaning process consists of the following steps:

1. Copy the original datasets to the folder "0 Data"

```{r copyFiles, eval=F}
# Path of original file
pathOrders <- "orders/order_data.csv"
# Path of original file to be pasted into the Data folder
newPathOrders <- "0 Data/order_data_R.csv"
# Path of the cleaned file
pathOrdersClean <- "0 Data/order_data_cleaned_R.csv"
# Path of the small version of the clean file
pathOrdersSmall = "0 Data/order_data_small_R.csv"
# Path of the headers
pathOrderHeaders <- "orders/order_columns.txt"

pathClicks <- "clickstream/clickstream_data.csv"
pathClicks2 <- "clickstream/clickstream_data_part_2.csv"
newPathClicks <- "0 Data/clickstream_data_R.csv"
newPathClicks2 <-"0 Data/clickstream_data_part_2_R.csv"
pathClicksClean  <- "0 Data/clickstream_data_cleaned_R.csv"
pathClicksSmall = "0 Data/clickstream_data_small_R.csv"
pathClicksHeaders <- "clickstream/clickstream_columns.txt"

# 1) Copy csv to data folder
file.copy(pathClicks, newPathClicks, overwrite = TRUE )
file.copy(pathClicks2, newPathClicks2, overwrite = TRUE )
file.copy(pathOrders, newPathOrders, overwrite = TRUE )
pathOrders <- newPathOrders
pathClicks <- newPathClicks
pathClicks2 <- newPathClicks2
```

2. Read the data, add headers (i.e. column labels), replace "?" and "NULL" with NA, drop columns which have a 100% ratio of missing data, reformat datetime cells and save the result (e.g. as "order_data_cleaned_R.csv")

```{r cleanFiles, eval=F}
# 2) read files, set headers and replace ? with NA

# Function to get headers from header.txt
getHeaders = function(filepath) {
    headers <- list()
    i <-1
    con <- file(filepath, "r")
    while ( TRUE ) {
        line <- readLines(con, n = 1)
        header <- gsub(":.*$","",line)
        if ( length(line) == 0 ) {
            break
        }
        headers[[i]] <- header
        i <- i+1
    }
    close(con)
    return(headers)
}

# get headers in an array
orderHeaders <- getHeaders(pathOrderHeaders)
clickHeaders <- getHeaders(pathClicksHeaders)

# read files, set headers, replace ? with NA and reformat time and date
orders <- read.csv(file=pathOrders, header=FALSE)

orders[orders=="?"]<-NA
orders[orders=="NULL"]<-NA
colnames(orders) <- orderHeaders
# drop columns which have only NA values
orders <- orders[,colSums(is.na(orders))<nrow(orders)]
# reformate date and time
for (col in names(orders)){
  if (grepl("Time",col)==TRUE){
    orders[,col]=gsub("\\\\", "", orders[,col])
  }
}
# save as new csv
write.table(orders, file = pathOrdersClean, sep=",", row.names=FALSE)

clicks <- read.csv(file=pathClicks, header=FALSE)
clicks2 <- read.csv(file=pathClicks2, header=FALSE)
clicks <- rbind(clicks,clicks2) 
clicks[clicks=="?"]<-NA
clicks[clicks=="NULL"]<-NA
colnames(clicks) <- clickHeaders
clicks <- clicks[,colSums(is.na(clicks))<nrow(clicks)]
for (col in names(clicks)){
  if (grepl("Time",col)==TRUE){
    clicks[,col]=gsub("\\\\", "", clicks[,col])
  }
}
write.table(clicks, file = pathClicksClean, sep=",", row.names=FALSE)
```

3. Create a subset of the cleaned data, containing only 1000 rows, and save it (e.g. as "order_data_small_R.csv")

```{r smallFiles, eval=F}
# 3) Save smaller versions for readability and dev purposes
small_size = min(1000,nrow(orders))
orders_small = orders[1:small_size,]
write.table(orders_small, file = pathOrdersSmall, sep=",", row.names=FALSE)

small_size = min(1000,nrow(clicks))
clicks_small = clicks[1:small_size,]
write.table(clicks_small, file = pathClicksSmall, sep=",", row.names=FALSE)
```

The same cleaning process has been implemented in Python. In the following block you can see a commented version of the python code. To execute it copy the content to your preferred Python IDE (e.g. Visual Studio Code, PyCharm, Atom), uncomment it and execute it. 

Note: The original script was located in the folder "./1 Data Preprocessing/Python/", as such the paths have to be adjusted if you created your script in another location. 

```{r pythonCode, eval=F}
# import shutil
# import pandas as pd
# 
# #paths
# pathOrders = "../../orders/order_data.csv"
# newPathOrders = "../../0 Data/order_data_P.csv"
# pathOrdersClean = "../../0 Data/order_data_cleaned_P.csv"
# pathOrdersSmall = "../../0 Data/order_data_small_P.csv"
# pathOrdersHeaders = "../../orders/order_columns.txt"
# 
# pathClicks = "../../clickstream/clickstream_data.csv"
# pathClicks2 = "../../clickstream/clickstream_data_part_2.csv"
# newPathClicks = "../../0 Data/clickstream_data_P.csv"
# pathClicksClean = "../../0 Data/clickstream_data_cleaned_P.csv"
# pathClicksSmall = "../../0 Data/clickstream_data_small_P.csv"
# pathClicksHeaders = "../../clickstream/clickstream_columns.txt"
# 
# pathMerge = "../../0 Data/merged_P.csv"
# pathMergeSmall = "../../0 Data/merged_small_P.csv"
# 
# #null values
# nan = float('nan')
# 
# def headers(path):
#     headers = open(path).\
#               read().\
#               split("\n")
#     for counter, header in enumerate(headers):
#         headers[counter] = (header.split(":"))[0]
#         if not header: #for empty rows
#             headers.pop(counter)
#     return headers
# 
# def clean(df):
#     #write NANs, delete empty columns
#     df = df. \
#          replace(to_replace="?", value=nan). \
#          replace(to_replace="NULL", value=nan). \
#          dropna(axis=1, how="all")
#     #Clean Time and Date
#     for column in df.columns:
#         if "Time" in column:
#             df[column] = df[column].\
#                          str.\
#                          replace('\\', '', regex=True)
#     return df
# 
# # Copy files
# shutil.copy(pathClicks, newPathClicks)
# shutil.copy(pathOrders, newPathOrders)
# 
# pathOrders = newPathOrders
# pathClicks = newPathClicks
# 
# # Read headers
# clicksHeaders = headers(pathClicksHeaders)
# ordersHeaders = headers(pathOrdersHeaders)
# 
# # Read data
# clicks = pd.read_csv(pathClicks, sep=",", names=clicksHeaders, dtype=str, encoding="ISO-8859-1")
# clicks2 = pd.read_csv(pathClicks2, sep=",", names=clicksHeaders, dtype=str, encoding="ISO-8859-1")
# clicks = clean(clicks.append(clicks2))
# orders = clean(pd.read_csv(pathOrders, sep=",", names=ordersHeaders, dtype=str, encoding="utf-8"))
# 
# # Save to CSV
# clicks.to_csv(path_or_buf=pathClicksClean, index=False)
# (clicks.head(1000)).to_csv(path_or_buf=pathClicksSmall, index=False)
# print("Clickstream:" + str(clicks.shape))
# orders.to_csv(path_or_buf=pathOrdersClean, index=False)
# (orders.head(1000)).to_csv(path_or_buf=pathOrdersSmall, index=False)
# print("Orders:" + str(orders.shape))
# 
# #Merging
# mergedData = pd.merge(clicks, orders,  how='inner', left_on=['Session ID'], right_on=['Order Session ID'])
# print(list(mergedData.columns.values))
# print(list(mergedData.shape))
# mergedData.to_csv(path_or_buf=pathMerge, index=False)
# (mergedData.head(10000)).to_csv(path_or_buf=pathMergeSmall, index=False)
```

##Testing the Difference Between Data Cleaned with Python and R {#diff}
To test if the cleaning scripts in Python and R result in the same file, execute the following code in RStudio. The package creates a diff view 

```{r diffFiles, eval=F}
library(diffobj)
pathOrders <- "0 Data/order_data_cleaned_R.csv"
pathClicks  <- "0 Data/clickstream_data_cleaned_R.csv"
pathOrdersPython <- "0 Data/order_data_cleaned_P.csv"
pathClicksPython  <- "0 Data/clickstream_data_cleaned_P.csv"

orders <- read.csv(file=pathOrders)
clicks <- read.csv(file=pathClicks)
clicksP = read.csv(file=pathClicksPython,na.strings=c("","NA"))
diffPrint(target=clicksP,current=clicks)
ordersP = read.csv(file=pathOrdersPython,na.strings=c("","NA"))
diffPrint(target=ordersP,current=orders)
```

#Analyzing the Data {#analysis}

The aim of the data analysis is to extract information, which is suspected to be valuable to the online shop, and prepare it in a way that makes it easily "digestible". The overview of the information is presented in one of the following two ways:

* A statistical table: Given a subset of interesting columns we create two statistical tables: One table for numerical columns in the subset and another for factors. The statistical table for the numerical columns contains the maximum value, minimum value, mean, median and standard deviation for each numerical column. The other one contains the five most frequent factors as well as the percentage of NAs and other factors for each factor column.
* A plot: Some information is too complex to be compressed into a single table without making it too confusing, or it's simply easier to understand if presented as a plot. The plot types used are time series plots, stacked bar plots, distribution curves, lorenz curves and maps.

##How much Data is Missing? {#missingData}

Before creating overview tables or plots for columns, it makes sense to look which columns actually contain a large quantity of information and which do not. To do a check up on the ratio of filled cells, we created a ranking for both datasets containing column names and the percentage of missing data for each column. Columns with a low percentage of missing data are then preferred in later analysis steps. The resulting rankings can be seen in the following two code blocks.

```{r NARankingOrders}
pathOrders <- "0 Data/order_data_cleaned_R.csv"
pathClicks  <- "0 Data/clickstream_data_cleaned_R.csv"
pathOrdersPython <- "0 Data/order_data_cleaned_P.csv"
pathClicksPython  <- "0 Data/clickstream_data_cleaned_P.csv"

pathNULLAnalysisOrders <- "2 Data Analysis/NAorders.csv"
pathNULLAnalysisClicks <- "2 Data Analysis/NAclicks.csv"

orders <- read.csv(file=pathOrders)
clicks <- read.csv(file=pathClicks)

# Create a DF to save the column names and appropriate NA percentage values
NAorders <- data.frame(matrix(ncol = 2, nrow = 0))
x <- c("Column_Name", "NA_percentage")
colnames(NAorders) <- x

# Get the NA percentage errors
for (column in names(orders)){
    percentageNA <- round(sum(is.na(orders[,column]))/length(orders[,column]),digits=4)
    NAorders[nrow(NAorders) + 1,] = list(column,percentageNA)
}
# Sort by NA percentage ascending
NAorders <- NAorders[with(NAorders, order(NAorders$NA_percentage)),]
kable(NAorders, row.names = FALSE)
```

```{r NARankingClicks}
# Create a DF to save the column names and appropriate NA percentage values
NAclicks <- data.frame(matrix(ncol = 2, nrow = 0))
x <- c("Column_Name", "NA_percentage")
colnames(NAclicks) <- x

# Get the NA percentage errors
for (column in names(clicks)){
    percentageNA <- round(sum(is.na(clicks[,column]))/length(clicks[,column]),digits=4)
    NAclicks[nrow(NAclicks) + 1,] = list(column,percentageNA)
}
# Sort by NA percentage ascending
NAclicks <- NAclicks[with(NAclicks, order(NAclicks$NA_percentage)),]
write.table(NAclicks, file = pathNULLAnalysisClicks, sep=",", row.names=FALSE)
kable(NAclicks, row.names = FALSE)
```

##Looking at the Orders Data {#analysisOrders}

The order data can be mainly devided into 4 sections:

* Customer Data: For this section we regard all information referring to the customer as an individual. 
```{r ordersCustomers, echo=FALSE}
interestingColumns <- c("City",
                        "Country",
                        "US.State",
                        "Age",
                        "Marital.Status",
                        "Gender",
                        "Audience",
                        "Truck.Owner",
                        "RV.Owner",
                        "Motorcycle.Owner",
                        "Working.Woman",
                        "Presence.Of.Children",
                        "Speciality.Store.Retail",
                        "Oil.Retail.Activity",
                        "Bank.Retail.Activity",
                        "Finance.Retail.Activity",
                        "Miscellaneous.Retail.Activity",
                        "Upscale.Retail",
                        "Upscale.Speciality.Retail",
                        "Retail.Activity")
cat(paste('-',interestingColumns), sep = '\n') 
```
    

##Looking at the Clicks Data {#analysisClicks}

#Creating a Model {#model}

#Summary {#summary}






