---
title: "Data analysis: ebuy's sales data"
bibliography: "bibliographies/literature.bib"
output:
  bookdown::html_document2:
    toc: yes
    theme: spacelab
---

# Data Manipulation
```{r includse01, message=FALSE}
library(dplyr)
library(ggplot2)
library(tidyr)
```

# Summary Statistics

# Plots

# Comparison of Groups
After loading the "experimental_results" dataset we decided to keep the first ID column.
```{r loadexpdata, message=FALSE}
experimentDf <- read.csv(file="../experiment/experimental_results.csv", sep=",", na.strings=c("NA"))
partialExperimentDf <- experimentDf[c("id_",
                                      "ranking_based",
                                      "random_recommendations",
                                      "profit_oriented")]

names(partialExperimentDf)[1] <- "id"
partialExperimentDf$id <- as.factor(partialExperimentDf$id)
summary(partialExperimentDf)
```

We then compared the results of both the ranking-based as well as the profit-oriented recommender systems against the results of the baseline recommender system (that selects products randomly).
```{r}
t.test(partialExperimentDf$random_recommendations, partialExperimentDf$ranking_based)
t.test(partialExperimentDf$random_recommendations, partialExperimentDf$profit_oriented)
```
The mean values (i.e. sales) of the profit-oriented recommender system and the baseline recommender system are not equal (p<0.00001), while the same hypothesis could not be rejected for the comparison of the ranking-based and the baseline recommender system (p=0.08). As the profit-oriented recommender systems mean value (21.75) is greater than the baseline mean (17.91), ebuy should preferably use the profit-oriented one.


# Models and Prediction
To train our models and make predictions we have to load additional libraries:
```{r includse02, message=FALSE}
library(caret)
library(tidyverse)
library(rpart)
library(rpart.plot)
```

## Load Data and Recode Variables
We first load the data and pick the columns that we are interested in:
```{r}
orderDf <- read.csv(file="../data/interim/orders/orders_cleaned.csv", sep=",", na.strings=c("?","NA", "NULL"))
partialOrdersDf <- orderDf[c("Product_Family_ID",
                             "Order_Line_Day_of_Week",
                             "Order_Line_Hour_of_Day",
                             "Order_Line_Amount",
                             "Product_ID",
                             "Gender",
                             "US_State",
                             "Age")]
```

Some of the variables have to be forced to be categorical:
```{r}
partialOrdersDf$Product_Family_ID <- as.factor(partialOrdersDf$Product_Family_ID)
partialOrdersDf$Order_Line_Day_of_Week <- as.factor(partialOrdersDf$Order_Line_Day_of_Week)
partialOrdersDf$Order_Line_Hour_of_Day <- as.factor(partialOrdersDf$Order_Line_Hour_of_Day)
partialOrdersDf$Gender <- as.factor(partialOrdersDf$Gender)
partialOrdersDf$US_State <- as.factor(partialOrdersDf$US_State)
partialOrdersDf$Age <- as.numeric(partialOrdersDf$Age)
summary(partialOrdersDf)
```

## Training the Model
As ebuy's products fall into certain product families, we trained a model that allows to predict for a new customer from which product family he will purchase a product. We first grew a large tree with a complexity parameter of cp=0.0001 (i.e. splits had to decrease the lack of fit by a factor of 0.00001):
```{r}
tree <- rpart(Product_Family_ID ~ Order_Line_Day_of_Week + Gender + Age,
              method="class",
              data=partialOrdersDf,
              cp=0.00001)
```

We then examined the results of a 10-fold cross-validation by plotting the complexity parameter vs. its cross-validated error (as shown in figure \@ref(fig:cpplottree1)).
```{r cpplottree1, echo=FALSE, fig.cap="Product Family ID: Complexity parameter vs. cross-validated error"}
plotcp(tree)
```

To prevent over-fitting, @kabacoff2015 suggests to choose the leftmost cp value below the dotted line (here: cp=0.001): a tree of that size (here: 41 splits) is the smallest tree whose cross-validated error is whithin one standard error of the minimum cross-validated error value. We therfore pruned the tree to its new size and pretty-printed the resulting tree (figure \@ref(fig:prunedtree1)).
```{r prunedtree1, echo=FALSE, fig.cap="Product Family ID: Pruned Classification Tree"}
prune(tree, cp=0.001) %>%
  prp(.)
```

Next we computed a linear regression model that helped us understand, how the different properties of customers affected the amount of money they would spend in total.
```{r}
# enable cross validation and set the number of folds:
ctrl <- trainControl(method = "cv",
                     number = 10)

# preform a linear regression:
linreg1 <- train(Order_Line_Amount ~ Age + Gender,
                 data = partialOrdersDf,
                 trControl = ctrl,
                 na.action  = na.pass,
                 method = "lm")
linreg1
linreg1$finalModel
```

# Summary

# Literature
