---
title: "Descriptive statistics for Products"
output: pdf_document
---

## What are the most ordered products in the data set?
```{r include=FALSE}
library(dplyr)
library(ggplot2)
orderDf <- read.csv(file="../data/interim/orders/orders_cleaned.csv", sep=",")
clickstreamDf <- read.csv(file="../data/interim/clickstream/clickstream_cleaned.csv", sep=",")
```
To figure this out we first load the data sets and choose all relevant columns:
```{r}
partialOrdersDf <- orderDf[c("Order_Session_ID", "Product_Object_ID",
                             "Product_ID", "Order_Line_Unit_List_Price", "Order_Day_of_Week",
                             "Product_Creation_Date", "Product_Family_ID")]

partialClickstreamDf <- clickstreamDf[c("Session_ID", "Product_Object_ID",
                                        "Product_ID", "Request_Date")]
```

```{r include=FALSE}
# force certain variables to be categorical:
partialOrdersDf$Order_Session_ID <- factor(partialOrdersDf$Order_Session_ID)
partialOrdersDf$Product_Object_ID <- factor(partialOrdersDf$Product_Object_ID)
partialOrdersDf$Product_ID <- factor(partialOrdersDf$Product_ID)
partialOrdersDf$Product_Family_ID <- factor(partialOrdersDf$Product_Family_ID)

partialClickstreamDf$Session_ID <- factor(partialClickstreamDf$Session_ID)
partialClickstreamDf$Product_Object_ID <- factor(partialClickstreamDf$Product_Object_ID)
partialClickstreamDf$Product_ID <- factor(partialClickstreamDf$Product_ID)
```

We then pick the 15 Product_IDs with the highest frequency count (which is introduced by dplyr as 'n') while
ignoring all '?' IDs
```{r}
mostOrderedProductsDf <- partialOrdersDf %>%
  count(Product_ID) %>%
  arrange(desc(n)) %>%
  slice(2:16)
```

and plot them (using the 'identity' stat to provide our own frequency count as y axis):
```{r}
ggplot(data = mostOrderedProductsDf) +
  geom_bar(mapping = aes(x = Product_ID, y = n), stat = "identity")
```


## What are the products most clicked on?
In an analogous fashion, we pick the most clicked products (again by their product ID)
```{r}
mostClickedProductsDf <- partialClickstreamDf %>%
  count(Product_ID) %>%
  arrange(desc(n)) %>%
  slice(2:16)
```

and plot those:
```{r}
ggplot(data = mostClickedProductsDf) +
  geom_bar(mapping = aes(x = Product_ID, y = n), stat = "identity")
```
Although the product with the ID 10315 is clicked more often than any other product, it is interestingly not the ordered most often.


## What are the top-selling product families?
A frequency count of all orders by their Product_Family_ID yields the top-selling product families:
```{r}
mostOrderedProductFamiliesDf <- partialOrdersDf %>%
  count(Product_Family_ID) %>%
  arrange(desc(n)) %>%
  slice(1:15)
head(mostOrderedProductFamiliesDf)
```

The winner clearly is product family 12295, which is also represented nicely in the corresponding plot:
```{r}
ggplot(data = mostOrderedProductFamiliesDf) +
  geom_bar(mapping = aes(x = Product_Family_ID, y = n), stat = "identity")
```


## How are orders distributed among the different days of the week?
To plot a frequency distribution of all orders over the days of week we first reorder the days in the
canonical way and then do a count the usual way:
```{r}
dowDf <- partialOrdersDf %>%
  mutate(Order_Day_of_Week = factor(Order_Day_of_Week, levels=c("Monday", "Tuesday", "Wednesday",
                                                                "Thursday", "Friday", "Saturday",
                                                                "Sunday"))) %>%
  count(Order_Day_of_Week) %>%
  slice(1:7)
```

We can then simply plot as before:
```{r}
ggplot(data = dowDf) +
  geom_bar(mapping = aes(x = Order_Day_of_Week, y = n), stat = "identity")
```


\pagebreak
## Are certain product families bought more often on certain days of the week?
To figure this out we plot the product Product_Family_ID vs. its frequency count (which is performed 'under the hood' by ggplot) and add the order day as a facet:
```{r}
ggplot(data = partialOrdersDf) +
  geom_bar(mapping = aes(x = Product_Family_ID)) +
  facet_wrap(~ Order_Day_of_Week)
#TODO: only print the x most frequent product family IDs!
```


## What are the most and least expensice products?
To find the most expensive product we can with the help of dplyr select the maximum as follows:
```{r}
partialOrdersDf %>%
  filter(Order_Line_Unit_List_Price == max(Order_Line_Unit_List_Price)) %>%
  distinct(Product_Object_ID, .keep_all = TRUE) %>%
  select(Product_Object_ID, Order_Line_Unit_List_Price)
```

We can find the least expensive one by looking at the minimum respectively:
```{r}
partialOrdersDf %>%
  filter(Order_Line_Unit_List_Price == min(Order_Line_Unit_List_Price)) %>%
  distinct(Product_Object_ID, .keep_all = TRUE) %>%
  select(Product_Object_ID, Order_Line_Unit_List_Price)
```
