---
title: "Kims Report"
author: "Kim Ferres"
date: "23-05-2019"
bibliography: literature.bib 
output:
  bookdown::html_document2:
    toc: yes
    toc_float: true
    theme: flatly
---

```{r importingMyLibraries, echo=FALSE}
  #    ^ only output, not coding
  #cmd+alt+i --> for r coding
  #load libraries
  library(tidyverse)
  library(ggplot2)
  library(dplyr)
  library(knitr)
```
#Prologue

#Introduction {#introduction}

##Motivation
##Expected Results


#Data Import

The `diamonds` dataset has `r nrow(diamonds)` observations.
```{r basicInformationDiamonds, echo=FALSE}
  #filter, use diaondswith a certain cut
  premium_diamonds <- diamonds %>%
    filter(cut=="Premium")
```

The `premium_diamonds` dataset has `r nrow(premium_diamonds)` observations.

#Descriptive Statistics
##Tables

```{r myTables}
  kable(head(diamonds)) #kableextra
  df <- data.frame(x=1:10, y=11:20, z=101:110)
  summary_stats <- df %>% #start with the data frame, and then...
    summarize_at(
      .vars = c("x", "y", "z"), #select varibles for table
      .funs = funs(min, max, mean, median, sd) #summary statistics for table
      
    ) %>% 
    gather(key,value) %>%
    separate(col=key, sep="_", c("feature", "stat")) %>%
    spread(key=stat, value=value) #repeated obeservations in multiple columns
  kable(summary_stats)
```

What about factors?

```{r myTables2}
  kable(head(diamonds)) #kableextra
  df <- data.frame(x=1:10, y=11:20, z=101:110, cat=c("cat1","cat2")) %>% filter(cat=="cat1")
  summary_stats <- df %>% #start with the data frame, and then...
    summarize_at(
      .vars = c("x", "y", "z"), #select varibles for table
      .funs = funs(min, max, mean, median, sd) #summary statistics for table
    ) %>% 
    gather(key,value) %>%
    separate(col=key, sep="_", c("feature", "stat")) %>%
    spread(key=stat, value=value) #repeated obeservations in multiple columns
  kable(summary_stats)
  
```


##Figures

Figure \@ref(fig:plot) shows carat information against price.
Figure \@ref(fig:plot2) shows the table information against price
Section  \@ref(introduction) was the Introduction.

```{r plot, echo=FALSE, fig.cap="Carat against price"}
  #   ^ names must not include underscores
  ggplot(data=diamonds, aes(x=carat, y=price)) +
    geom_point() +
    theme_bw()
```

```{r plot2, echo=FALSE, fig.cap="Carat against table"}
  ggplot(data=diamonds, aes(x=carat, y=table)) +
    geom_point() +
    theme_bw()
```

The number of observations $n=$ `r nrow(diamonds)`. A simple formula: $\sum{i=1}^n = 100$

$$
\begin{equation}
\lim\limits{x \to \infty \exp(-x)=0}
\end{equation}
$$
$$
\begin{equation}
\lim\limits{x \to \infty \exp(-x)=0}
(#eq:someMath)
\end{equation}
$$

It is trivial to show that \@ref(eq:someMath) is correct.
Previous work(@R-base) has shown that it is wrong.


#Summary



#Literature






